Appendix 2: Manuscript and Exploratory Code

### 2025-06-10 manuscript_code.Rmd
multigroup analysis

---
title: "Appendix 2: Manuscript and Exploratory Code"
author: "Abigail Edwards, Lauri Hietajärvi and Mikko Arvas"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time())`"
output:
  pdf_document:
    toc: yes

always_allow_html: true
---

@@

```{r}
data %>% filter(bd04 < 0)
data %>% filter(bd03 > 12)

@@

@@

@@

```{r}
gglikert(
  data, 
  include =   starts_with("po") 
)
```

@@

```{r}
gglikert(
  data, 
  include =   starts_with("si") 
)
```

@@

```{r}
gglikert(
  data, 
  include =   starts_with("ac") 
)
```

@@

```{r}
gglikert(
  data, 
  include =   starts_with("ai") 
)
```

@@

```{r}
gglikert(
  data, 
  include =   starts_with("iv") 
)
```

@@

```{r}
eval=FALSE

@@

eval=FALSE

@@

eval=FALSE

@@

```{r}
#Bivariate correlation table for paper

@@

### a) Sum score model with robust estimator and listwise deletion

eval=FALSE
#if (fitmodels) {
  #fit.po02ss <- sem(po02ss.model,  
                    #estimator = "MLR", 
                    #missing = "listwise",
                    #data = data.fit2,
                    #auto.fix.first = FALSE, 
                    #std.lv = TRUE,
                    #fixed.x = TRUE

@@

eval=FALSE
#lavaan::inspect(fit.po02ss,"r2")

@@

```{r}
eval=FALSE
#fit.po02ss.est  <-standardizedSolution(fit.po02ss)
#fit.po02ss.est %>% select(-label,se,z) %>%  filter(op == '~')

@@

```{r}
eval=FALSE
#fit.po02ss.est  <-standardizedSolution(fit.po02ss)
#fit.po02ss.est %>% 
  #filter(abs(est.std) < 0.3) %>% 
  #select(-z,-se) %>% 
  #arrange(abs(est.std)) %>% 
  # Just the loadings
  #filter(op != '~1')

@@

###  c) Sum score model with robust estimator and fiml

```{r}
eval=FALSE
#if (fitmodels) {
  #fit.po04ss <- sem(
    #po02ss.model,  
    #estimator = "MLR", 
    #data = data.fit2, 
    #auto.fix.first = FALSE,
    #std.lv = TRUE,
    #missing = "fiml",
    #fixed.x = FALSE 
  #)
  #models[['fit.po04ss']] <- fit.po04ss
#}

@@

```{r}
eval=FALSE
#fit.po04ss.est  <-standardizedSolution(fit.po04ss)
#fit.po04ss.est %>% select(-label,se,z) %>%  filter(op == '~')

@@

```{r}
eval=FALSE
#fit.po04ss.est %>% 
  #filter(abs(est.std) < 0.3) %>% 
  #select(-z,-se) %>% 
  #arrange(abs(est.std)) %>% 
  # Just the loadings
  #filter(op != '~1')

@@

```{r}
eval=FALSE
#lavaanPlot(
  #model = fit.po04ss, 
   #labels = labelsforplottingnull,
  #node_options = list(shape = "box", fontname = "Helvetica"), 
  #edge_options = list(color = "grey"), 
  #coefs = TRUE, 
  #stand = TRUE,
  #sig=0.001
  #) %>% lavaanPlot::embed_plot_pdf(here("figures/plsssem04.pdf"))

@@

###  d) Sum score model with bootstrapping and fiml

```{r}
eval=FALSE
#if (fitmodels) {
  #fit.po05ss <- sem(
    #po02ss.model,  
    #estimator = "ML", 
    #bootstrap = nBoots,
    #se = "boot",
    #data = data.fit2, 
    #auto.fix.first = FALSE,
    #std.lv = TRUE,
    #missing = "fiml",
    #fixed.x = FALSE 
  #)
  #models[['fit.po05ss']] <- fit.po05ss
#}

@@

```{r}
eval=FALSE
#fit.po05ss.est  <-standardizedSolution(fit.po05ss)
#fit.po05ss.est %>% select(-label,se,z) %>%  filter(op == '~')

@@

```{r}
eval=FALSE
#fit.po05ss.est %>% 
  #filter(abs(est.std) < 0.3) %>% 
  #select(-z,-se) %>% 
  #arrange(abs(est.std)) %>% 
  # Just the loadings
  #filter(op != '~1')

@@

eval=FALSE
#lavaanPlot(
  #model = fit.po05ss, 
   #labels = labelsforplottingnull,
  #node_options = list(shape = "box", fontname = "Helvetica"), 
  #edge_options = list(color = "grey"), 
  #coefs = TRUE, 
  #stand = TRUE,
  #sig=0.001
  #) %>% lavaanPlot::embed_plot_pdf(here("figures/plsssem05.pdf"))

@@

### e) Latent factor model with robust estimator and listwise deletion

```{r}
eval=FALSE
#if (fitmodels) {
  #fit.po02 <- sem(po02.model,  
                  #estimator = "MLR",
                  #missing = "listwise",
                  #data = data.fit2,
                  #auto.fix.first = FALSE,
                  #std.lv = TRUE,
                  #fixed.x = TRUE
  #)
  #models[["fit.po02"]] <- fit.po02
#}
#lavaan::summary(fit.po02,standardized = TRUE)

@@

```{r}
eval=FALSE
#lavaan::inspect(fit.po02,"r2")

@@

```{r}
eval=FALSE
#fit.po02.est  <-standardizedSolution(fit.po02)
#fit.po02.est %>% select(-label,se,z) %>%  filter(op == '~')

@@

```{r}
eval=FALSE
#fit.po02.est %>% 
  #filter(abs(est.std) < 0.3) %>% 
  #select(-z,-se) %>% 
  #arrange(abs(est.std)) %>% 
  # Just the loadings
  #filter(op != '~1')

@@

```{r}
labelsforplotting <- c(
  "psycown" = "Psychological ownership",
  "selfid"  = "Self-identity",
  "intention" = "Intention",
  "blooddonor" = "Blood donation history"
)

@@

### f) Latent factor model with boostrapping and listwise deletion

@@

```{r}
#fit.po03.best <- parameterEstimates(fit.po03)
#fit.po03.best %>% select(-se,-z) %>% filter(op == "~")

@@

```{r}
#lavaanPlot(
  #model = fit.po03, 
   #labels = labelsforplotting,
  #node_options = list(shape = "box", fontname = "Helvetica"), 
  #edge_options = list(color = "grey"), 
  #coefs = TRUE, 
  #stand = TRUE,
  #sig=0.001
  #) %>% lavaanPlot::embed_plot_pdf(here("figures/pllvsem03.pdf"))

@@

#Exploratory Analysis (a1*b1 comparison)

@@

#exploratory analysis (multigroup analysis to explore impact of gender)

@@

#end of exploratory analysis
#knitr::knit_exit()

@@

@@

```{r}
#fit.po05.est  <-standardizedSolution(fit.po05)
#fit.po05.est %>% select(-label,se,z) %>%  filter(op == '~')

@@

```{r}
#fit.po05.est %>% 
  #filter(abs(est.std) < 0.3) %>% 
  #select(-z,-se) %>% 
  #arrange(abs(est.std)) %>% 
  # Just the loadings
  #filter(op != '~1')

@@

```{r}
#lavaanPlot(
  #model = fit.po05, 
   #labels = labelsforplotting,
  #node_options = list(shape = "box", fontname = "Helvetica"), 
  #edge_options = list(color = "grey"), 
  #coefs = TRUE, 
  #stand = TRUE,
  #sig=0.001
  #) %>% lavaanPlot::embed_plot_pdf(here("figures/pllvsem05.pdf"))

>>>>

---
title: 'Appendix 2: Manuscript and Exploratory Code'
author: "Abigail Edwards, Lauri Hietajärvi and Mikko Arvas"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time())`"
output:
  html_document:
    toc: true
    df_print: paged
  pdf_document:
    toc: true
always_allow_html: true
---

@@

```{r eval = FALSE}
data %>% filter(bd04 < 0)
data %>% filter(bd03 > 12)

@@

```{r eval = FALSE}

@@

```{r eval=FALSE}

@@

```{r eval=FALSE}
gglikert(
  data, 
  include =   starts_with("po") 
)
```

@@

```{r eval=FALSE}
gglikert(
  data, 
  include =   starts_with("si") 
)
```

@@

```{r eval=FALSE}
gglikert(
  data, 
  include =   starts_with("ac") 
)
```

@@

```{r eval=FALSE}
gglikert(
  data, 
  include =   starts_with("ai") 
)
```

@@

```{r eval=FALSE}
gglikert(
  data, 
  include =   starts_with("iv") 
)
```

@@

```{r eval=FALSE}

@@

```{r eval=FALSE}

@@

include=FALSE

@@

```{r echo = FALSE}
#Bivariate correlation table for paper

@@

# a) Sum score model with robust estimator and listwise deletion

```{r echo = FALSE}

#if (fitmodels) {
  #fit.po02ss <- sem(po02ss.model,  
                    #estimator = "MLR", 
                    #missing = "listwise",
                    #data = data.fit2,
                    #auto.fix.first = FALSE, 
                    #std.lv = TRUE,
                    #fixed.x = TRUE

@@

```{r echo = FALSE}

#lavaan::inspect(fit.po02ss,"r2")

@@

```{r echo = FALSE}

#fit.po02ss.est  <-standardizedSolution(fit.po02ss)
#fit.po02ss.est %>% select(-label,se,z) %>%  filter(op == '~')

@@

```{r echo = FALSE}

#fit.po02ss.est  <-standardizedSolution(fit.po02ss)
#fit.po02ss.est %>% 
  #filter(abs(est.std) < 0.3) %>% 
  #select(-z,-se) %>% 
  #arrange(abs(est.std)) %>% 
  # Just the loadings
  #filter(op != '~1')

@@

#  c) Sum score model with robust estimator and fiml

```{r echo = FALSE}
#if (fitmodels) {
  #fit.po04ss <- sem(
    #po02ss.model,  
    #estimator = "MLR", 
    #data = data.fit2, 
    #auto.fix.first = FALSE,
    #std.lv = TRUE,
    #missing = "fiml",
    #fixed.x = FALSE 
  #)
  #models[['fit.po04ss']] <- fit.po04ss
#}

@@

```{r echo = FALSE}

#fit.po04ss.est  <-standardizedSolution(fit.po04ss)
#fit.po04ss.est %>% select(-label,se,z) %>%  filter(op == '~')

@@

```{r echo = FALSE}

#fit.po04ss.est %>% 
  #filter(abs(est.std) < 0.3) %>% 
  #select(-z,-se) %>% 
  #arrange(abs(est.std)) %>% 
  # Just the loadings
  #filter(op != '~1')

@@

```{r echo = FALSE}

#lavaanPlot(
  #model = fit.po04ss, 
   #labels = labelsforplottingnull,
  #node_options = list(shape = "box", fontname = "Helvetica"), 
  #edge_options = list(color = "grey"), 
  #coefs = TRUE, 
  #stand = TRUE,
  #sig=0.001
  #) %>% lavaanPlot::embed_plot_pdf(here("figures/plsssem04.pdf"))

@@

#  d) Sum score model with bootstrapping and fiml

```{r echo = FALSE}

#if (fitmodels) {
  #fit.po05ss <- sem(
    #po02ss.model,  
    #estimator = "ML", 
    #bootstrap = nBoots,
    #se = "boot",
    #data = data.fit2, 
    #auto.fix.first = FALSE,
    #std.lv = TRUE,
    #missing = "fiml",
    #fixed.x = FALSE 
  #)
  #models[['fit.po05ss']] <- fit.po05ss
#}

@@

```{r echo = FALSE}

#fit.po05ss.est  <-standardizedSolution(fit.po05ss)
#fit.po05ss.est %>% select(-label,se,z) %>%  filter(op == '~')

@@

```{r echo = FALSE}

#fit.po05ss.est %>% 
  #filter(abs(est.std) < 0.3) %>% 
  #select(-z,-se) %>% 
  #arrange(abs(est.std)) %>% 
  # Just the loadings
  #filter(op != '~1')

@@

```{r echo = FALSE}

#lavaanPlot(
  #model = fit.po05ss, 
   #labels = labelsforplottingnull,
  #node_options = list(shape = "box", fontname = "Helvetica"), 
  #edge_options = list(color = "grey"), 
  #coefs = TRUE, 
  #stand = TRUE,
  #sig=0.001
  #) %>% lavaanPlot::embed_plot_pdf(here("figures/plsssem05.pdf"))

@@

# e) Latent factor model with robust estimator and listwise deletion

```{r echo = FALSE}
#if (fitmodels) {
  #fit.po02 <- sem(po02.model,  
                  #estimator = "MLR",
                  #missing = "listwise",
                  #data = data.fit2,
                  #auto.fix.first = FALSE,
                  #std.lv = TRUE,
                  #fixed.x = TRUE
  #)
  #models[["fit.po02"]] <- fit.po02
#}
#lavaan::summary(fit.po02,standardized = TRUE)

@@

```{r echo = FALSE}

#lavaan::inspect(fit.po02,"r2")

@@

```{r echo = FALSE}

#fit.po02.est  <-standardizedSolution(fit.po02)
#fit.po02.est %>% select(-label,se,z) %>%  filter(op == '~')

@@

```{r echo = FALSE}

#fit.po02.est %>% 
  #filter(abs(est.std) < 0.3) %>% 
  #select(-z,-se) %>% 
  #arrange(abs(est.std)) %>% 
  # Just the loadings
  #filter(op != '~1')

@@

```{r echo = FALSE}
labelsforplotting <- c(
  "psycown" = "Psychological ownership",
  "selfid"  = "Self-identity",
  "intention" = "Intention",
  "blooddonor" = "Blood donation history"
)

@@

# f) Latent factor model with boostrapping and listwise deletion

```{r echo = FALSE}

@@

```{r echo = FALSE}
#fit.po03.best <- parameterEstimates(fit.po03)
#fit.po03.best %>% select(-se,-z) %>% filter(op == "~")

@@

```{r echo = FALSE}
#lavaanPlot(
  #model = fit.po03, 
   #labels = labelsforplotting,
  #node_options = list(shape = "box", fontname = "Helvetica"), 
  #edge_options = list(color = "grey"), 
  #coefs = TRUE, 
  #stand = TRUE,
  #sig=0.001
  #) %>% lavaanPlot::embed_plot_pdf(here("figures/pllvsem03.pdf"))

@@

### Exploratory Analysis (a1*b1 comparison)

@@

### exploratory analysis (multigroup analysis to explore impact of gender)

@@

#end of exploratory analysis
knitr::knit_exit()

@@

```{r echo = FALSE}

@@

```{r echo = FALSE}
#fit.po05.est  <-standardizedSolution(fit.po05)
#fit.po05.est %>% select(-label,se,z) %>%  filter(op == '~')

@@

```{r echo = FALSE}
#fit.po05.est %>% 
  #filter(abs(est.std) < 0.3) %>% 
  #select(-z,-se) %>% 
  #arrange(abs(est.std)) %>% 
  # Just the loadings
  #filter(op != '~1')

@@

```{r echo = FALSE}
#lavaanPlot(
  #model = fit.po05, 
   #labels = labelsforplotting,
  #node_options = list(shape = "box", fontname = "Helvetica"), 
  #edge_options = list(color = "grey"), 
  #coefs = TRUE, 
  #stand = TRUE,
  #sig=0.001
  #) %>% lavaanPlot::embed_plot_pdf(here("figures/pllvsem05.pdf"))
